\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
rewording configuration time sentences

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time. E1 participants' configuration time was a small fraction of connection time because because they generally chose a configuration that successfully connected to Tor right away, and the time spent bootstrapping the connection to Tor dominated the connection time. E3 participants' configuration time was significantly less than their connection time they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts. E2, participants' configuration time was a a modest amount of their connection time, due to the combination of reasons that affected participants in E1 and E3.

Due to the mentions above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.

>>>>

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time. E1 participants' configuration time was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away. E3 participants' configuration time was also dominated by the time waiting for a connection to be established to Tor because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts. E2 participants' configuration time was a a fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.

Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.
